Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-13 awipev-CO2.Rmd
last updates with salinity name variable in awipev-co2.rmd

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
```

@@

sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
  dplyr::filter(sal_fb >28)
sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
      dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%

@@

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
# print(poster_temp)
# #
# png("figures/poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# #
# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# #
#    grid(lty=1)
# #
#    par(new = T)
# #
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#     lwd = "months")
#      box()
#      dev.off()
# 
# 
# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# #
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)

  #at != "2307.05" & sal_fb > 28, !is.na(at))

@@

#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
  #print(at_s)

@@

# Salinity is a predictor of AT -> using the regression defined above
d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
```

@@

#interpolation of salinity during the FB off maintenance
sal_fbinterp <-approx(d_all$datetime, d_all$sal_fb, xout=d_all$datetime, method="linear", rule=2)
names(sal_fbinterp) <- c("datetime", "sal_fb_interp")
sal_fbinterp <- as.data.frame(sal_fbinterp)
d_all$sal_fb_interp <- sal_fbinterp$sal_fb_interp

d_all$sal_fb <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_fb_interp, d_all$sal_fb)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
                          calT = d_all$temp_insitu, calSal = d_all$sal_fb )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_fb_interp)

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("ct", label = "ct", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("at", label = "at", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
  #dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
            sal_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
            sal_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
kable(range_month)
```

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

<!-- p_sal <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(sal_fb >28),aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_temp_fb <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=temp_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Temperature (in Ferrybox)", x="Time")+ ylim(c(-2.5, 9.5)) + -->
<!--         theme_bw() -->
<!--  p_pco2 <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(pco2_contros < 450),aes(x=datetime, y=pco2_contros),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected pCO2", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_ta_raw <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_sf <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pHint_tot_sf),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_df <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pH_durafet_),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sal.png", p_sal,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_temp_fb.png", p_temp_fb,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_pco2.png", p_pco2,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sf.png", p_sf,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_df.png", p_df,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_ta.png", p_ta,width = 15, height = 5 ,units="cm") -->

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
```

@@

sal_xts <- dplyr::select(d_all, datetime, sal)%>%
  dplyr::filter(sal >28)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%

@@

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
# print(poster_temp)
# #
# png("figures/poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# #
# plot(sal ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# #
#    grid(lty=1)
# #
#    par(new = T)
# #
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#     lwd = "months")
#      box()
#      dev.off()
# 
# 
# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# #
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal>30 ), aes(x=datetime,y=sal), colour="sal") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, month,closest_datetime, at, sal)%>%
  dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)

  #at != "2307.05" & sal > 28, !is.na(at))

@@

#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
fit <- lm(data = d_all_at_discrete, at ~ sal)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()

at_s <- ggplot(d_all_at_discrete,aes(x=sal, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
  #print(at_s)

@@

# Salinity is a predictor of AT -> using the regression defined above
d_all$at_calc <- slope_s_at * d_all$sal + intercept_s_at
```

@@

#interpolation of salinity during the FB off maintenance
salinterp <-approx(d_all$datetime, d_all$sal, xout=d_all$datetime, method="linear", rule=2)
names(salinterp) <- c("datetime", "sal_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_interp <- salinterp$sal_interp

d_all$sal <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_interp, d_all$sal)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
                          calT = d_all$temp_insitu, calSal = d_all$sal )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_interp)

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("ct", label = "ct", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("at", label = "at", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
  #dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
            sal_max = round(max(sal, na.rm=TRUE), digits = 2),
            sal_min = round(min(sal, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
kable(range_month)
```

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal,temp_fb,temp_insitu, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal,temp_fb,temp_insitu, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

<!-- p_sal <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(sal >28),aes(x=datetime, y=sal),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_temp_fb <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=temp_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Temperature (in Ferrybox)", x="Time")+ ylim(c(-2.5, 9.5)) + -->
<!--         theme_bw() -->
<!--  p_pco2 <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(pco2_contros < 450),aes(x=datetime, y=pco2_contros),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected pCO2", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_ta_raw <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=sal),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_sf <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pHint_tot_sf),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_df <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pH_durafet_),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sal.png", p_sal,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_temp_fb.png", p_temp_fb,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_pco2.png", p_pco2,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sf.png", p_sf,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_df.png", p_df,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_ta.png", p_ta,width = 15, height = 5 ,units="cm") -->
